\pdftitle

### 2018-07-27 nips_2018_author_response.tex
update text and scripts

\begin{document}
We thank the reviewers for their analysis, appreciative words, and suggestions.

\textbf{Reviewer 1}
\begin{enumerate}
\item It would be interesting to use the frequency distribution of the
  sample activity, measured in the recording, as a constraint, equivalent
  to $n$ moment constraints. In fact, using it at the population level is
  less questionable than using at the sample level (activities with zero
  frequencies lead to zeroes in the maximum-entropy distribution, and these
  are unreasonable because the sample size is much smaller than the
  state-space size. This indicates that maximum-entropy is used beyond its
  range of validity). Its use, however, addresses a different question than
  the one discussed in our introduction, namely to define and measure
  \enquote{cooperativity} by comparing maximum-entropy distributions
  constructed from different numbers of moments.
\item Unfortunately the reviewer forgot the bibliographic reference to Tkacik et al
  2012. We'd like to read that paper.
\item It's true, we forgot to discuss how the population-level application
  solves the sample-size-dependence of maximum-entropy results pointed out in
  previous literature. This should be addressed in an amended version of
  the paper.
\end{enumerate}

@@

\textbf{Reviewer 3}
\begin{enumerate}
\item We agree with the Reviewer that the main formulae of the paper, (17)
  and (19), probably have little \emph{experimental} use today. But the
  formulae and the analysis behind them are important exactly for the
  points raised by the Reviewer:
  \begin{itemize}
  \item \begin{minipage}[t]{0.8\linewidth} the Reviewer says \enquote{the
        differences between the sample level and population level
        distribution seem minor} -- this can be true, but we could not have
      known this, if we hadn't faced the whole problem and derived a
      formula showing that the difference is minor;
    \end{minipage}
  \item
    \begin{minipage}[t]{0.8\linewidth}
      application of the method with higher-order constrains can show more
      interesting differences between sample- and population-level
      distributions. See e.g. the plot on the right. This should be added
      in an amended version of the paper. Unfortunately there are space
      constraints.
    \end{minipage}\hspace{\fill}
    \smash{\begin{minipage}[c]{0.19\linewidth}\vspace{0pt}
      \includegraphics[width=\linewidth]{zoom_4mom.png}
    \end{minipage}}

%     % \setlength{\intextsep}{0.5ex}% with wrapfigure
%     \begin{figure}[h!]%{r}{0.4\linewidth} % with wrapfigure
%   \centering
% %\caption{***}\label{fig:comparison_a5}
% \end{figure}
  \item The population-level distribution can be more or less entropic of
    the sample-level one. is actually \emph{less} entropic. By
    lifting the constraints to the population level, the maximum-entropy
    principle allows us to explore even \emph{more entropic} sample
    distributions than those allowed by a direct application at the sample
    level. Thus this approach agrees with the \enquote{maximum entropy}
    spirit. -- These points should be mentioned, of course, in an amended
    version of the paper.
  \item 
  \end{itemize}
\item We agree with Reviewer 3 that the paper emphasizes some philosophical
  aspects; intentionally so. Sadly we can't make all kinds of readers
  happy; a choice of audience is necessary. As readers ourselves we
  appreciate when a paper begins by asking: \enquote{What is the question?
    is it possible to translate it into a mathematical problem? which
    principles can we use to make such translation?}. There are papers that
  develop very refined mathematical techniques but leave us unsatisfied,
  with the lingering question \enquote{why are we doing this?}. This is the
  reason why we try to emphasize these kinds of questions. But we are sure
  that part of the NIPS audience will appreciate this emphasis.

\end{enumerate}
\end{document}

>>>>

\begin{document}
We thank the reviewers for their analysis, appreciative words, and
suggestions. We reply to major points only. The manuscript can be easily
amended to address the points we don't discuss here.

\textbf{Reviewer 1}
\begin{enumerate}
\item It would be interesting to use the frequency distribution of the
  sample activity, measured in the recording, as a constraint, equivalent
  to $n$ moment constraints. In fact, using it at the population level is
  less questionable than using at the sample level (activities with zero
  frequencies lead to zeroes in the maximum-entropy distribution, and these
  are unreasonable because the sample size is much smaller than the
  state-space size. This indicates that maximum-entropy is used beyond its
  range of validity). Its use, however, addresses a different question than
  the one discussed in our introduction, namely to define and measure
  \enquote{cooperativity} by comparing maximum-entropy distributions
  constructed from different numbers of moments.
\item It's true, we forgot to discuss how the population-level application
  solves the sample-size-dependence of maximum-entropy results pointed out in
  previous literature. This should be addressed in an amended version of
  the paper.
\end{enumerate}

@@

\textbf{Reviewer 3}
\begin{enumerate}
\item We agree with the Reviewer that the main formulae of the paper, (17)
  and (19), probably have little \emph{experimental} use today. But the
  formulae and the analysis behind them are important exactly for the
  points raised by the Reviewer:
  \begin{itemize}
  \item \begin{minipage}[t]{0.74\linewidth}The Reviewer says \enquote{the
        differences between the sample level and population level
        distribution seem minor}: this could be true, but we could not have
      known this, if we hadn't faced the whole problem and derived a
      formula showing that the difference is minor.
    \end{minipage}\hspace{\fill}
    \smash{\begin{minipage}[t]{0.24\linewidth}\vspace{0pt}
      \includegraphics[width=\linewidth]{zoom_4mom.png}
    \end{minipage}}
  \item
    \begin{minipage}[t]{0.74\linewidth}
      Application of the method with higher-order constrains can show more
      interesting differences between sample- and population-level
      distributions. See e.g. the plot on the right: the bimodal
      distribution is the marginalized, population-level one.
    \end{minipage}
%     % \setlength{\intextsep}{0.5ex}% with wrapfigure
%     \begin{figure}[h!]%{r}{0.4\linewidth} % with wrapfigure
%   \centering
% %\caption{***}\label{fig:comparison_a5}
% \end{figure}
\item Calculations show that the population-level distribution can be less
  or more entropic than the sample-level one. But a more entropic
  distribution is not necessarily more correct (we could just use a uniform
  distribution then). The question is how the constraints are appropriately
  applied in the method. 
\end{itemize}
As this Reviewer and Reviewer 2 remark, the points and findings above
deserve more discussion. Unfortunately there are space constraints, and we
preferred to give more room to a careful analysis of the principles behind
the method, to see whether the method is correctly applied. Our main wish
is that our readers will give more thoughts to these matters. We could
hurry up and produce a lot of mathematical results; but, whether positive or
negative, such would be meaningless if the method isn't meaningfully
applied. And it isn't always the case that a meaningful application of a
method can be judged by its results alone.
% \item We agree with Reviewer 3 that the paper emphasizes some philosophical
%   aspects; intentionally so. Sadly we can't make all kinds of readers
%   happy; a choice of audience is necessary. As readers ourselves we
%   appreciate when a paper begins by asking: \enquote{What is the question?
%     is it possible to translate it into a mathematical problem? which
%     principles can we use to make such translation?}. There are papers that
%   develop very refined mathematical techniques but leave us unsatisfied,
%   with the lingering question \enquote{why are we doing this?}. This is the
%   reason why we try to emphasize these kinds of questions. But we are sure
%   that part of the NIPS audience will appreciate this emphasis.
\end{enumerate}
\end{document}
